Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-07 introductory.tex
cleaned up the beginning bits a bit more.

This paper is an extension of [Anonymous Paper by Anonymous Auhthors] which was published as a NIER paper in [Anonymous Conference]. The current paper extends that paper in the following ways: 
\begin{itemize}
  \item Providing more details about the case study (in Section \ref{sec:case}) and extending the data collection period with half year
  \item A better categorization of the dashboard perspectives presented in Sections \ref{sec:util}, \ref{sec:grouping}, \ref{sec:evolution} including several new perspectives
  \item A detailed discussion on automated outlier detection and monitoring (Section \ref{sec:outliers})
  \item An advanced discussion integration continuous integration environments in order to triangulate the live collected data with information from testing the endpoints with a constant load and introduce a mechanism for performance prediction (Section \ref{sec:testing})
  \item A discussion on the overhead incurred by the presented tool \ml{(... if we make it... )}
\end{itemize}

>>>>

This paper is an extension of [Anonymous Paper by Anonymous Auhthors] which was published as a NIER paper in [Anonymous Conference]. The current paper extends that paper in the following ways: 
\begin{itemize}
  \item Providing more details about the case study in Section \ref{sec:case} and extending the data collection period with half year
  \item Novel perspectives and a better categorization of the perspectives presented in Sections \ref{sec:utilandperf} -- \ref{sec:evolution}
  \item A detailed discussion on automated outlier detection and monitoring (Section \ref{sec:outliers})
  \item An advanced discussion integration continuous integration environments in order to triangulate the live collected data with information from testing the endpoints with a constant load and introduce a mechanism for performance prediction (Section \ref{sec:testing})
  \item A more extended discussion about lessons learned while developing the tool including measurements on the overhead incurred by the presented tool \ml{(... if we make it... )}
\end{itemize}

### 2018-04-07 paper.tex
cleaned up the beginning bits a bit more.

\author{
\IEEEauthorblockN{The Author, The Other Author}\\
Institute\\
University, Country\\
Email: \{author\}@university.domain 
}

>>>>

\author{
\IEEEauthorblockN{Author One, Segundo Autor, Troisi\`eme Auteur}\\
Famous Institute for Software Engineering and Computer Science\\
University of Great City, Some Country\\
Email: \{first.last\}@university.to 
}
